Transparent Changes

### 2022-05-20 scripts/comparison.Rmd
Update comparison script

# Get data files

files <- list.files("../data/ramptests", full.names = TRUE)
```

@@

```{r calc, eval = FALSE}
# ZAN raw data only saves imprecise body mass data in the raw data file.
info <- read.csv("../data/participants.csv")

# level 1: iterate over each data file
results <- purrr::map_dfr(
  .x = seq_along(files),
  .f = function(n) {
    # level 2: iterate over each processing method
    data <- spiro(files[n], weight = info$bodymass[n])
    purrr::map_dfc(
      .x = c("bm", "tm", "tb"), 
      .f = function(method, data) {
        # level 3: iterate over each parameter range
        purrr::map_dfc(
          .x = seq.int(5,60),
          .f = vo2max,
          method = method,
          data = data
        )
      }, 
      data = data
    )
  }
)

@@

>>>>

# Get data files
files <- list.files("../data/ramptests", full.names = TRUE)

# ZAN raw data only saves imprecise body mass data in the raw data file.
info <- read.csv("../data/participants.csv")
```

@@

```{r calc, eval = FALSE}
# level 1: iterate over each data file
results <- purrr::map_dfr(
  .x = seq_along(files),
  .f = function(n) {
    # level 2: iterate over each processing method
    data <- spiro(files[n], weight = info$bodymass[n])
    purrr::map_dfc(
      .x = c("bm", "tm", "tb"), 
      .f = function(method, data) {
        # level 3: iterate over each parameter range
        purrr::map_dfc(
          .x = seq.int(5,60),
          .f = vo2max,
          method = method,
          data = data
        )
      }, 
      data = data
    )
  }
)

@@

## Calculate zero phase digital filter

```{r}
# Function to get VO2max with digital filtering
get_fzmax <- function(i) {
  dta <- spiro(files[i], weight = info$bodymass[i])
  spiro_max(dta, smooth = "0.04fz3")$VO2_rel
}

# iterate over all tests
fzmax <- purrr::map_dbl(seq_along(files), get_fzmax)

# normalize to reference procedure
fzmax_norm <- fzmax / res$tb_30

# get median and quantile values
median(fzmax_norm)
quant(fzmax_norm, 0.1, 0.9)
```
